SST_patterns

### 2020-01-20 SST_patterns.Rmd
Testing

```{r}
knitr::opts_chunk$set(
  comment = "R>",
  warning = FALSE,
  message = FALSE 
)
#update.packages() 
library(tidyverse)
library(lubridate)
library(ggpubr)
library(zoo)
library(FNN)
library(scales)
library(gridExtra)
library(circular)
library(fossil)
library(mapproj)
# library(ncdf4) # This was used to process NetCDF files in an earlier version
library(stringr)
library(doMC); doMC::registerDoMC(cores = 4)
library(fasttime)
library(xtable)
library(ncdf4) # library for processing netCDFs
library(data.table)
# library(plyr) # RWS: Never load the plyr package as it interferes with the tidyverse
library(heatwaveR)
```

@@

Combined_frequency <- Combined_frequency %>% 
  mutate(t = parse_date(date, format = "%b_%Y"),
         distance = factor(distance))

@@

distance_corr <- Combined_frequency %>% 
  group_by(site) %>% 
  slope_calc()
```

>>>>

```{r}
knitr::opts_chunk$set(
  comment = "R>",
  warning = FALSE,
  message = FALSE 
)
#update.packages() 
library(tidyverse)
library(lubridate)
library(ggpubr)
library(zoo)
library(FNN)
library(scales)
library(gridExtra)
library(circular)
library(fossil)
library(mapproj)
library(broom)
# library(ncdf4) # This was used to process NetCDF files in an earlier version
library(stringr)
library(doMC); doMC::registerDoMC(cores = 4)
library(fasttime)
library(xtable)
library(ncdf4) # library for processing netCDFs
library(data.table)
# library(plyr) # RWS: Never load the plyr package as it interferes with the tidyverse
library(heatwaveR)
```

@@

# Combined_frequency <- Combined_frequency %>% 
  # mutate(t = parse_date(date, format = "%b_%Y"),
         # distance = factor(distance))

@@

distance_corr <- Combined_frequency %>% 
  group_by(site, product) %>% 
  slope_calc()
```
